Twitter Trader - Correlating \\ Stocks with Twitter Activity

### 2012-11-16 paper/paper.tex
updated paper

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\nocopyright
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\noindent We will develop a system to collect the most recent set of tweets related to one company at any point in time and provide an aggregate binary classification of the set with a confidence rating. The classification and confidence value will provide a heuristic for potential investments. We may augment this heuristic by incorporating recent trends in stock prices and/or Twitter sentiment.

Second paragraph.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}
\nocopyright
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\noindent We will develop a system to aggregate tweets about a set of companies using a classifier. Each tweet about a company will be labeled with a sentiment {positive, negative, neutral}. We hope to use the classifications and confidences to provide a heuristic for potential investments by analyzing the sentiment of tweets about a company over time. We may augment this heuristic by incorporating recent trends in stock prices and/or Twitter sentiment.
